analysis-pilot

### 2023-08-16 code/analysis-pilot.Rmd
first spaghetti

#so like a third mismatch, and only a couple off by more than 1
```
# Prep accuracy

@@

# accuracy graph
```{r}
accuracy <- filtered_data %>% 
  group_by(game) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100, percent = signif(fraction, 2))

>>>>

#so like a third mismatch, and only a couple off by more than 1
```
# timed_transcripts editing
```{r}
timed_new <- timed_transcripts %>% 
  filter(!speaker %in% c("I", "M", "i")) %>% 
  filter(!trialNumStart %in% c(0.0, 0.5, 1.0, 13.0, NA)) %>% 
  mutate(wordCount = str_count(text, "\\S+"), roundStart = ceiling(trialNumStart))

View(timed_new)

# timed_new graphing
```{r}
# filter trials
# geom line - color = game OR group = game
ggplot(timed_new, aes(x = roundStart, y = wordCount, group = game, color = game)) + 
  geom_line() +
  labs(color = "Game ID", x = "Round #", y = "Utterance Count") +
  #scale_x_continuous(#breaks=seq(1,10,1), limits = c(2,13)) +
  #ylim(120, 200) + 
  theme_classic()

# Prep accuracy

@@

# accuracy graph
```{r}
accuracy <- filtered_data %>% 
  group_by(game) %>% 
  summarize(total=n(),
            correct=sum(countCorrect)) %>% 
  mutate(fraction = correct/total*100, percent = signif(fraction, 2)) 
  View(accuracy)
